Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-02 draft/paper1.tex
Update the ellipticity and color gradient figure
New paper1

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    With these deeper data, we show definitively that at fixed stellar mass,
    massive central galaxies display mass density profiles that are not self similar, 
    with the accreted fraction increasing towards unity for galaxies in our highest 
    stellar mass bin. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.
    \song{First trial by Jenny; need more works}

@@

    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter 
    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
    open questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation 
    scenario (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
    instabilities or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the 
    so-called ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller 
    effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, 
    Cimatti2008}), slightly higher central velocity dispersion and stellar mass 
    density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like 
    morphologies (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies and a large fraction of these massive progenitors become 
    quiescent at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase in the ``two-phase'' formation scenario is driven by 
    non-dissipative processes such as dry mergers with other galaxies 
    (e.g. \citealt{Naab2006, Khochfar2006}). 
    \update{
    To explain the observed significant increase of $R_{\mathrm{e}}$ (e.g. 
    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
    scenario suggests that minor mergers should dominate the mass assembly during 
    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
    Laporte2013}).
    More importantly, both numerical simulation (e.g. \citealt{Oser2010}) and 
    semi-analytic model (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction of the accreted component should increase with total stellar mass, 
    although different models still predict somewhat different values at fixed 
    stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    According to the recent results from Illustris \footnote{
    \texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}), the fraction of the 
    accreted mass increases significantly with total stellar mass at \logms{}$>11.0$, 
    and the accreted component starts to dominate the stellar mass budget 
    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
    }
%% ------------------------------------------------------------------------------------ %%

    \update{
    At the same time, some of these ``two-phase'' scenario's predictions still have 
    little observational constraint. 
    One-dimensional analysis used to conclude that \ser{} law can reasonably describe  
    the surface brightness (or stellar mass density) profiles of nearby massive 
    elliptical galaxies (e.g. \citealt{Kormendy2009}; except for the most central 
    region), and the \ser{} index seems to increase with total luminosity (or stellar 
    mass; e.g. \citealt{Graham2013}). 
    There was also suggestion that elliptical galaxies can be divided into two groups
    based on how well their 1-D surface brightness profiles can be described by \ser{}
    law (e.g. \citealt{Schombert2015}). 
    Meanwhile, recent two-dimensional analysis points out that the stellar distributions 
    of massive ETGs are better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}). 
    However, it is still not clear whether these 1-D or 2-D results are consistent with 
    the ``two-phase'' scenario. 
    One of the main limitation here is that one needs very deep observations for large 
    sample of massive ETGs to correctly estimate their total stellar mass 
    (e.g. \citealt{Bernardi2013, DSouza2014}) and study the assembly history via 
    their accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, Iodice2017}).
    Currently, such works are often limited by the shallow images such as the ones from
    the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or the small 
    sample size. 
    }

    In this paper, we take advantage of new high-resolution (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    \update{
    With the help of reliable spectroscopic and photometric redshift 
    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
    we select a large sample (${\sim} 7000$) of massive central galaxies at 
    $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
    HSC wide layer. 
    In this paper, we use this sample to 
    (a) measure individual \mden{} profiles for galaxies out to 100 kpc reliably with 
    the HSC data, 
    (b) examine the implications for the stellar mass function (SMF) when the outer 
    parts of galaxies are accounted for, and
    (c) investigate the dependence of their outer envelopes on stellar mass.    
    In a second paper in this series, we will further look into the potential 
    environmental dependence of structures in massive ETGs (Huang\etal in prep.).
    }

    %\jenny{I suggest removing this here. I do not think it belongs in the Intro:
    %Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
    %providing appropriate model to describe the \mstar{} distribution of massive 
    %galaxy from its center to the very outskirt, we focus on \mstar{} within two 
    %different physical apertures in this work:}
    %\song{Since the original paper is quite long and complicated, we decide to define
    %the two aperture masses in the beginning, and explain why they are important.
    %For the new draft, I think it is Ok to do this later, but more comments on this 
    %are welcomed!}

%    \begin{itemize}
%    
%        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
%            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
%            builds up the inner, dense core of massive ETGs.  
%            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
%            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
%            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
%            We use \minn{} as a proxy for the mass forged during the ``in-situ''
%            phase. 
%            Given the quality of the HSC data, we can reliably measure \minn{} over our 
%            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
%            0.3 and 0.5).  
%            
%        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
%            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
%            $\times R_{\mathrm{e}}$. 
%            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
%            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
%            ``total'' \mstar{}. 
%            Although not perfect, we argue that our measurements of \mtot{} (which are 
%            actually measuring the light directly out to 100 kpc) are a better tracer 
%            of total \mstar{} than model-dependent results from shallower data 
%            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
%            out to large radii.
%            
%       \end{itemize}}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover ${\sim} 1400$ deg$^2$ 
    in 5 broad bands ($grizY$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the $i$-band 
    than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec), and the wide area, the HSC survey represents a tremendous dataset to 
    perform large statistical study of the surface brightness profiles of ETGs out to 
    large radii.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{BoschInPrep}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the the total flux of massive ETGs (this is discussed further in 
    \citealt{BoschInPrep}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    Here we limit our study to the very high-mass end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} galaxy cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team\footnote{It is created by matching HSC objects with all publicly available 
    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
    The spec-z quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.}.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    \update{
    For objects without a spectroscopic redshift, we match them with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius, 
    and keep the matched objects with useful red-sequence photo-$z$ 
    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
    These galaxies are the best candidates for BCGs in clusters selected from 
    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    }
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. 
    Before we can define our mass-complete sample of central galaxies required for 
    our analysis, we describe our one-dimensional photometric analysis 
    (\S \ref{sec:ellipse}) and stellar mass estimations (\S \ref{sec:mstar}). 
    We then define the final sample in \S \ref{sec:final}.

@@

%% ------------------------------------------------------------------------------------ %%  
%\subsection{The \redm{}{} cluster catalog}
%    \label{ssec:redmapper}
%    
%    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
%    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
%    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
%    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
%    These authors have developed a well-tested red-sequence cluster finder that has 
%    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
%    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
%    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
%    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
%    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
%    their associated membership probabilities. 
%    Details about the performance of the \redm{}~cluster catalog can be found in 
%    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
%    Several studies have published calibrations between the \redm{}~richness estimate, 
%    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
%    Melchior2016}). 
%    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
%    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
%    The \redm{} catalog therefore helps us group massive central galaxies into 
%    samples with different average \mhalo{}. 
%    We will use the central galaxies of \redm{} clusters 
%    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
%    live in massive halos.
%% ------------------------------------------------------------------------------------ %% 
%
%% ------------------------------------------------------------------------------------ %% 
%  \begin{figure}
%      \centering 
%      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
%      \caption{
%          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
%      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
%      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
%          On average, \mcmodel{} underestimates the total stellar mass of massive 
%          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
%          Vertical histograms indicate the mass difference for galaxies with
%          $11.6<$\logmtot{}$<11.9$. 
%          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
%          function. 
%          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
%          of the total luminosity whereas solid lines correspond to the SMF computed
%          using the total luminosity from our 1-D profile. 
%          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
%          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
%          (red lines).
%          \song{New figure for completeness; Need to update the caption}
%          }
%      \label{fig:mass_complete}
%  \end{figure}

>>>>

    Massive galaxies are important to our understanding of galaxy formation, and 
    their extended stellar halos contain crucial fossil records of their assembly 
    history. 
    In this work, we use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), 
    high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) 
    survey to investigate the surface mass density profiles and outer stellar halos 
    of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow images and/or over-simplified models like the \texttt{CModel} tend to 
    miss the extended stellar halo and result in underestimated stellar mass in a 
    mass-dependent way.  
    It will impact important applications like the measurements of the stellar mass 
    function. 
    With these deeper data, we explicitly show that at fixed stellar mass,
    massive central galaxies display surface mass density profiles that are not 
    self-similar, with the outer-slope becoming shallower and the fraction of mass 
    in the outskirt increasing with total stellar mass.
    We also show that the ellipticity of the stellar halo increases with stellar
    mass, while the optical color gradients do not strongly depend on stellar mass.
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretions of small systems. 
    The surface mass density profiles are provided in a convenient tabulated format 
    in order to facilitate comparisons with predictions from numerical simulations 
    of galaxy formation.

@@

    Massive galaxies are fascinating objects that have experienced complex assembly 
    process and dramatic evolution.  
    They are crucial for both cosmology and the study of galaxy formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter 
    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
    open questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation 
    scenario (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the 
    population of massive quiescent galaxies at high redshift that have smaller 
    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
    vanDokkum2008, Cimatti2008}), slightly higher central velocity dispersion and 
    stellar mass density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and 
    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than their local 
    descendants (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
    mass.

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies. 
    A large fraction of these massive progenitors became quiescent at $z>1$ 
    (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase of their assembly is driven by non-dissipative processes such 
    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    To explain the observed increase of $R_{\mathrm{e}}$ (e.g. 
    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
    scenario suggests that minor mergers should dominate the mass assembly during 
    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
    Laporte2013}).
    Both numerical simulations (e.g. \citealt{Oser2010}) and 
    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction in the accreted component should increase with total stellar mass, 
    despite their technical differences (e.g. \citealt{Lackner2012, Cooper2013, 
    Qu2017}).
    For instance, recent result from the Illustris \footnote{
    \texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
    accreted stars increases significantly with total stellar mass at \logms{}$>11.0$, 
    and the accreted component starts to dominate the stellar mass budget 
    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
%% ------------------------------------------------------------------------------------ %%

    Given the success of this two-phase scenario in explaining trends like overall size 
    growth, it is time to confront their predictions with additional observations, 
    especially the detailed profiles of surface mass density and shape for low redshift 
    massive galaxies.  
    Early one-dimensional analysis of nearby massive ETGs suggest that the 
    single-\ser{} profile can describe their surface brightness (or surface mass 
    density) profiles reasonably well (e.g. \citealt{Kormendy2009}; except for the
    most central region), with the \ser{} index increasing with total luminosity 
    (e.g. \citealt{Graham2013}).
	However, the situation is in fact more complicated, with a suggestion from 
	\citet{Schombert2015} that there are actually two families of light profiles:
	the ones that follow single-\ser{} law well and the ones show significant 
	deviation.
	Two-dimensional analysis, meanwhile, finds that the stellar distributions 
    of massive ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}). 
    \citet{Huang2013b} further suggests a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar mass 
    (e.g. \citealt{Bernardi2013, DSouza2014}) and explore their assembly history via 
    their extended, accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).
    Currently, such work is limited by the depth of imaging from large-area surveys 
    such as the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or
    the small sample size of massive galaxies with deep images.

    In this paper, we take advantage of new high-quality (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of reliable spectroscopic and photometric redshift 
    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
    we select a large sample (${\sim} 7000$) of massive central galaxies at 
    $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
    In this paper, we use this sample to 
    (a) reliably measure individual surface mass density (\mden{}) profile of 
    massive galaxy out to 100 kpc, 
    (b) investigate the dependence of their outer stellar halos on total stellar 
    mass, and 
    (c) examine the implications for the stellar mass function (SMF) when the outer 
    halos of massive galaxies are accounted for.   
    In a second paper in this series, we will further look into the potential 
    environmental dependence of structures in massive ETGs (Huang\etal in prep.).

@@

    The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the 
    $i$-band surface brightness limit than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents a tremendous dataset to 
    perform large statistical study of the surface brightness profiles of massive
    galaxies out to their very outskirts.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{Bosch2017}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the the total flux of massive ETGs (this is discussed further in 
    \citealt{Bosch2017}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
      \caption{              
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
      	  galaxies (grey dots).
      	  The running-median of the mass differences along with the standard deviations
      	  in a series of mass bins are shown in large red, hexagons with error bars. 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for all galaxies (shaded 
          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
          The average difference is small (0.02 dex) and does not show 
          clear mass--dependence. 
          }
      \label{fig:mass_diff}
  \end{figure*}

@@

    Here we limit our study to the very high-mass end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} galaxy cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team\footnote{It is created by matching HSC objects with all publicly available 
    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
    The spec-$z$ quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.}.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    Objects without a spectroscopic redshift are matched with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
    We keep the matched objects with useful red-sequence photo-$z$ 
    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
    These galaxies are the best candidates for centrals in clusters selected from 
    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. and the GAMA survey provides additional $14$\% of spec-$z$.
    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
    10 kpc can be reliably measured; 
    (2) The background noise and cosmological dimming are not major issues and the 
    \mden{} profile can be measured out to $>100$ kpc; 
    (3) Evolution in structure and stellar population properties can be largely 
    ignored.  
    At both lower and higher redshift, the completeness of spec-$z$ sample starts 
    to decline.  
    Also for bright galaxies at lower redshift, the over-subtraction of background 
    becomes a more serious issue. 
    Before we can define our mass-complete sample of massive galaxies required for 
    our analysis, we describe our one-dimensional photometric analysis 
    (\S \ref{sec:ellipse}) and stellar mass estimations (\S \ref{sec:mstar}). 
    We then define the final sample in \S \ref{sec:final}.

@@

%% ------------------------------------------------------------------------------------ %%  
%\subsection{The \redm{}{} cluster catalog}
%    \label{ssec:redmapper}
%    
%    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
%    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
%    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
%    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
%    These authors have developed a well-tested red-sequence cluster finder that has 
%    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
%    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
%    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
%    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
%    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
%    their associated membership probabilities. 
%    Details about the performance of the \redm{}~cluster catalog can be found in 
%    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
%    Several studies have published calibrations between the \redm{}~richness estimate, 
%    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
%    Melchior2016}). 
%    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
%    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
%    The \redm{} catalog therefore helps us group massive central galaxies into 
%    samples with different average \mhalo{}. 
%    We will use the central galaxies of \redm{} clusters 
%    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
%    live in massive halos.
%% ------------------------------------------------------------------------------------ %%
